Prestige as a Driving Force in Cultural Transmission

### 2022-04-25 ms/PrestigeBias.tex
update

% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{
  \textbf{Robustness of DM approximations to inclusion of estimation error.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high estimation error rate. Markers for average across simulations, error bars for 95\% confidence intervals.
  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,x^2)$ where $x \in [10^{-7},10^{-1}]$.
  }	
  % maybe 50% CI looks better? the bars are too large to understand. maybe a wider y range? say from 0 to 0.02?
  \label{fig:hetro_error}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   High bias weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it). Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
	% TODO
	% see comments in previous figure
\end{figure}

@@

\begin{result}[Effective selection coefficient]
$1-\beta(A)$ is equivalent to the selection coefficient $s$ in the diffusion-equation approximation of the a classic Wright-Fisher model that approximate the fixation probability and fixation time of an advantageous allele.
\end{result}

@@

\begin{result}[Effective population size]
$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
\end{result}

@@

Using our substitute for a selection coefficient, $1-\beta$, and the effective population size $N_e$, we can estimate the fixation probability and time of our binary model.

The fixation probability derived from Kimura is therefore:
\begin{equation}\label{eq:kimura_p}
P_{fix} = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
\end{equation}

where $x$ is the initial frequency of the advantageous phenotype $\hat{A}$.

The time to fixation can be estimated by:
\begin{equation}\label{eq:kimura_t}
T_{fix}=\frac{1-P_{fix}}{1-\beta}\int_0^x\frac{e^{2(1-\beta) \xi}-1}{\xi(1-\xi)}d\xi+ \frac{P_{fix}}{1-\beta}\int_x^1\frac{1-e^{-2(1-\beta)(1-\xi)}}{\xi(1-\xi)}d\xi
\end{equation}
where the integrals cannot be solved in closed form, so we can only estimate them numerically.

To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
In \cref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
In \cref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations: \cref{eq:kimura_p} and \cref{eq:kimura_t}.

\begin{figure}[h]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
     \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size.
  Error bars show mean and 95\% confidence intervals.
  Effective population, $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point; Population size, $N=1,000$; $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
  % TODO
  % - better x and y label, as noted above
  % - in legend, replace "kimura" with "Approx."
  % - in legend, remove "=2s"
  % - change approximation color, it is too similar to WF simulations
  % - make the horizontal line black?
  % - caption should start with bold sentence summarizing the figure. 
  % - in caption add description of each parameter (as I did for N)
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[h]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  % TODO 
  % - see previous figure
  % - consider making the error bars smaller with more simulations or narrower CI (50%?)
  % - consider using plt.xscale('log')
  % - maybe you can merge this figure with the figure?
  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
  \label{fig:var_beta}
\end{figure}

\paragraph{Changing environment.}
After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.

@@

\paragraph{Proposition:} $E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$ , $V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.

The proof is based on the proof of \citet{changeEnv}, proving a similar scenario.
\paragraph{Proof by induction:}
From \cref{eq:expec_freq} we know that
\begin{equation}\label{eq:ch_1}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\
&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
\end{split}
\end{equation}
Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\
&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\
&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
\end{split}
\end{equation}

@@

We'll now look at the induction assumption to see that
\begin{equation}
E\left[\frac{X_t}{N}-x\right]=E\left[\frac{X_t}{N}\right]-E[x]=E\left[\frac{X_t}{N}\right]-x ,
\end{equation}
so using the assumption we get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\right] &\simeq \frac{1}{N} S_t x(1-x)+x \\
1 - E\left[\frac{X_t}{N}\right] &\simeq 1- \frac{1}{N} S_t x(1-x)+x
\end{split}
\end{equation}
we'll use both expressions in \cref{eq:ch_2} and get
\begin{equation}\label{eq:ch_3}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x)
\end{split}
\end{equation}
after again omitting $O(\frac{1}{N^2})$ parts of the equation.
To conclude our proof, we see that
\begin{equation}
E\left[\frac{X_{t+1}}{N}-x\right] = E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right]
\end{equation}
so again using the induction assumption, together with \cref{eq:ch_3} we get
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-x\right] &\simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
& \simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) \\
& \simeq \frac{1}{N} S_{t+1} x(1-x)
\end{split}
\end{equation}
which proves the first part of our preposition.

For the second part, we'll use a property of variance:
\begin{equation}\label{eq:ch_var}
V\left(\frac{X_{t+1}}{N}\right) = E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right)
\end{equation}

@@

Using the induction assumption and \cref{eq:ch_var2}:
\begin{equation}
V\left(\frac{X_{t+1}}{N}\right) \simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1)
\end{equation}
proving the second part of our preposition.

Following our proof, we can say that after many cycles, we can use a modified version of our fixation probability:
\begin{equation}
P_{fix} = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
\end{equation}
where $\frac{S_n}{n} = \frac{k-l}{k+l}(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.

\begin{figure}[h]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  %TODO remove the (a) and (b) from the latex and put them on the figure 	itself (top left corenr).
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{Model simulations compared with both the constant environment and the changing environment equations with different effective populations sizes and selection coefficients. Changing the effective population size doesn't affect the approximation, and it is condensed the mathematical expected values across all values. High values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values. Very high values ($s>0.35$) will even deviate from the constant environment expected values. This is expected because Kimura's approximation are only viable for low selection coefficient values.
  $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.9$, $J=1$, \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} bias weight is: $\alpha=0.1$. 
  }
   %TODO 
  % see previous figures..
  % not sure you need the green curve in the left panel
  % ANS - to show it's not a valid option to use?
  % the right panel might be better with yscale('log')? or xscale('log')? right now it is hard to see that the blue even changes...
  \label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_div_l.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
   \caption{}
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_min_l.pdf}
   \end{subfigure}
  \end{center}
  %TODO add panel labels (a) and (b) on figures corner.
  % see previous figures todos
  \caption{Model simulations compared with both the constant environment and the changing environment equations for different values of $k,l$, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation. 
 We ran $10,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.8$, $J=1$, $1-\beta=s=0.02$, $\alpha=0.1$.}
  \label{fig:ch_env_k_l}
\end{figure}

>>>>

% TODO maybe it would be better to compute a test score for multiple distributions and show it is lowest (highest?) for DM ? do model comparison this way?
% But what distributions? just some random distributions? (like normal and exponential? but what parameters?)

@@

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{
  \textbf{Robustness of DM approximations to inclusion of estimation error.} Both the DM approximation (orange) and Kimura's equation (black line) fit the stochastic simulations (blue) well even with a high estimation error rate. Markers for average across simulations, error bars for 95\% confidence intervals.
  5,000 simulations per data point; population size, $N=1000$; bias weight, $\alpha=0.1$; phenotype values, $\hat{A}=1$,$A=0.7$; bias strength parameter $J\sim N(1,x^2)$ where $x \in [10^{-7},10^{-1}]$.
  }	
  \label{fig:hetro_error}
\end{figure}

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
   \caption{\textbf{Robustness of DM approximations to variation in the bias weight $\alpha$.} 
   High bias weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it). Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
  $5000$ simulations per data point; population size, $N=1000$; trait bias normally distributed, $\alpha\sim N(0.5,x^2)$; phenotype values ,$\hat{A}=1$,$A=0.7$; success bias value, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
\end{figure}

@@

\begin{result}[Effective selection coefficient]\label{res:selection_coef}
$1-\beta(A)$ is equivalent to the selection coefficient $s$ in the diffusion-equation approximation of the a classic Wright-Fisher model that approximate the fixation probability and fixation time of an advantageous allele.
\end{result}

@@

\begin{result}[Effective population size]\label{res:effective_population}
$N_e=\alpha N + (1-\alpha)$, where $Ne$ is the effective population size of our binary model.
\end{result}

@@

\begin{result}[Fixation probability approximation]
The fixation probability is estimated by:
\begin{equation}\label{eq:kimura_p}
P_{fix} = \frac{1-e^{-2(1-\beta)N_e x}}{1-e^{-2(1-\beta)N_e}}
\end{equation}
where $x$ is the initial frequency of the advantageous phenotype $\hat{A}$.
\end{result}
\begin{proof}
Using our substitute for a selection coefficient, $1-\beta$, and the effective population size $N_e$, we can estimate the fixation probability using the diffusion equation, $E[X'-X]$ (\cref{res:selection_coef}), and $V(X'-X)$ (\cref{res:effective_population}).
\end{proof}

\begin{result}[Fixation time approximation]
\begin{equation}\label{eq:kimura_t}
T_{fix}=\frac{1-P_{fix}}{1-\beta}\int_0^x\frac{e^{2(1-\beta) \xi}-1}{\xi(1-\xi)}d\xi+ \frac{P_{fix}}{1-\beta}\int_x^1\frac{1-e^{-2(1-\beta)(1-\xi)}}{\xi(1-\xi)}d\xi
\end{equation}
\end{result}

\begin{proof}
Again using the diffusion equation and \cref{res:selection_coef,res:effective_population}, we get our result.
the integrals cannot be solved in closed form, so we can only estimate them numerically.
\end{proof}

\paragraph{Numeric validation.}
To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
In \cref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
In \cref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations: \cref{eq:kimura_p} and \cref{eq:kimura_t}.

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/kimura_var_alpha.pdf}
  \caption{\textbf{Goodness of fit of Kimura's approximation for varying bias weights.}
  The approximation (black) fits DM simulations results (green) and Wright Fisher simulation results (orange) when using \cref{eq:kimura_p}.
  Fixation probability (a) is limited at approximately $2s$ (blue), like the classic WF model.
  Markers for average values across $5,000$ simulations, error bars for 95\% confidence intervals.
   Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.7$; success coefficient, $1-\beta=s=0.044$.}
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/binary/kimura_var_beta.pdf}
  \caption{\textbf{Goodness of fit of Kimura's approximation for varying success coefficients.}
   The approximation (black) fits DM simulations results (green) and Wright Fisher simulation results (orange) when using \cref{eq:kimura_p}.
  Markers for average values across $5,000$ simulations, error bars for 75\% confidence intervals.
 Here, Population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=a\cdot \hat{A}, a \in [0.01,0.99]$; bias weight, $\alpha=0.01$.}
  \label{fig:var_beta}
\end{figure}

After finding good estimations for our model in a constant environment, when the favorable trait is always $\hat{A}$, we want to find an estimation for our model in a changing environment.

@@

\begin{result} [Expected difference in frequency in a changing environment]\label{res:ch_expected}
$E[\frac{X_t}{N}-x]\simeq \frac{1}{N}S_tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
\end{result}
\begin{result}[Variance of difference in frequency in a changing environment]\label{res:ch_var}
$V(\frac{X_t}{N})\simeq\frac{1}{N_e}tx(1-x)$, where $x$ is the initial frequency of the favorable/invading trait and $X_t$ is the number of individuals with the trait at time $t$.
\end{result}

\begin{proof}
Following the proof of \citet{changeEnv}, we prove by induction. We will prove \cref{res:ch_expected,res:ch_var} together, because the induction assumptions are needed for both.

From \cref{eq:expec_freq} we know that
\begin{equation}\label{eq:ch_1}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\bigg|X_t\right] &= \frac{X_t}{N}\left(1-\frac{X_t}{N}\right)(1-\beta_{t+1}) \\
&= \frac{1}{N}\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)s_{t+1}
\end{split}
\end{equation}
Also note that using the definition of $V(y)=E[y^2]-(E[y])^2$
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\left(1-\frac{X_t}{N}\right)\right] &= E\left[\frac{X_t}{N}-\left(\frac{X_t}{N}\right)^2\right] \\
&= E\left[\frac{X_t}{N}\right]-E\left[\left(\frac{X_t}{N}\right)^2\right] \\
&= E\left[\frac{X_t}{N}\right] - V\left(\frac{X_t}{N}\right) - \left(E\left[\frac{X_t}{N}\right]\right)^2
\end{split}
\end{equation}

@@

We'll now look at the induction assumption to see that
\begin{equation}
E\left[\frac{X_t}{N}-x\right]=E\left[\frac{X_t}{N}\right]-E[x]=E\left[\frac{X_t}{N}\right]-x ,
\end{equation}
so using the assumption we get
\begin{equation}
\begin{split}
E\left[\frac{X_t}{N}\right] &\simeq \frac{1}{N} S_t x(1-x)+x \\
1 - E\left[\frac{X_t}{N}\right] &\simeq 1- \frac{1}{N} S_t x(1-x)+x
\end{split}
\end{equation}
we'll use both expressions in \cref{eq:ch_2} and get
\begin{equation}\label{eq:ch_3}
\begin{split}
E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] &\simeq \frac{1}{N}s_{t+1} \left(\frac{1}{N} S_t x(1-x)+x \right)\left(1- \frac{1}{N} S_t x(1-x)+x \right) \\
&\simeq  \frac{1}{N}s_{t+1}\cdot x(1-x)
\end{split}
\end{equation}
after again omitting $O(\frac{1}{N^2})$ parts of the equation.
To conclude our proof, we see that
\begin{equation}
E\left[\frac{X_{t+1}}{N}-x\right] = E\left[\frac{X_{t+1}}{N}-\frac{X_t}{N}\right] + E\left[\frac{X_t}{N}-x\right]
\end{equation}
so again using the induction assumption, together with \cref{eq:ch_3} we get
\begin{equation}
\begin{split}
E\left[\frac{X_{t+1}}{N}-x\right] &\simeq \frac{1}{N}s_{t+1}\cdot x(1-x) + \frac{1}{N}S_t\cdot x(1-x) \\
& \simeq \frac{1}{N}x(1-x)(S_t + s_{t+1}) \\
& \simeq \frac{1}{N} S_{t+1} x(1-x)
\end{split}
\end{equation}
which proves \cref{res:ch_expected}.

For \cref{res:ch_var}, we'll use a property of variance:
\begin{equation}\label{eq:ch_var}
V\left(\frac{X_{t+1}}{N}\right) = E\left[V\left(\frac{X_{t+1}}{N} \bigg|X_t \right)\right] + V\left(E\left[\frac{X_{t+1}}{N} \bigg|X_t \right]\right)
\end{equation}

@@

Using the induction assumption and \cref{eq:ch_var2}:
\begin{equation}
V\left(\frac{X_{t+1}}{N}\right) \simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1)
\end{equation}
proving \cref{res:ch_var}.
\end{proof}

Following our proof, we can say that after many cycles, we can use a modified version of our fixation probability:
\begin{equation}\label{eq:ch_env}
P_{fix} = \frac{1-e^{-2 \frac{S_n}{n} N_e x}}{1-e^{-2 \frac{S_n}{n} N_e}}
\end{equation}
where $\frac{S_n}{n} = \frac{k-l}{k+l}(1-beta)$, $n=k+l$. Put into words, we use the average selection coefficient of a cycle ($k+l$) as the selection coefficient in our original equation.
In our proof we showed that the expected change in frequency and variance is only manifested in the selection coefficient $S_n$, and that we can use those modified equation as a base for Kimura's equation.

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var.pdf}
  \caption{\textbf{Robustness of approximation in a changing environment to varying success coefficient and success bias weight.}
 Markers for average values across $10,000$ simulations, error bars for (a) are 75\% confidence intervals, and 95\% for (b).
The approximation (blue) given by \cref{eq:ch_env} fits simulation results (orange) well when the effective population size varies (a).
On (b) we see that for high values of success bias ($s>0.1$) will distance the simulations from the changing environment expected values. Very high values ($s>0.35$) will even deviate from the constant environment expected values (green) given by \cref{eq:kimura_p}. This is expected because Kimura's approximation are only viable for low selection coefficient values.
  Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.9$; \textbf{(a)} success bias/selection coefficient is: $1-\beta=s=0.005$, \textbf{(b)} success bias weight is: $\alpha=0.1$. 
  }
  \label{fig:ch_env_alpha_beta}
\end{figure}

@@

\begin{figure}[h]
    \includegraphics[width=\linewidth]{../figures/changed_env/ch_env_var_k_l.pdf}
  \caption{\textbf{Robustness of approximation in a changing environment to varying sizes of the cycles.} 
Markers for average values across $10,000$ simulations, error bars are 95\% confidence intervals.
The approximation (blue) fits the simulations (orange) well for different sizes of the changing environment cycle, where $k$ is the number of generations where the bias is advantageous, and $l$ are the generations it is disadvantageous.
   When $k<l$ the approximation is good. When $k>l$, the approximation and the simulations are both very close to the constant environment approximation (green). 
 Here, population size, $N=1,000$; phenotype values, $\hat{A}=1$, $A=0.8$; success coefficient, $1-\beta=s=0.02$; success bias weight, $\alpha=0.1$.}
  \label{fig:ch_env_k_l}
\end{figure}
